The Numerical Accuracy of Computing Electrostatic Interaction in the Inhomogeneous and Correlated Molecular Systems: for the Ewald Summation, SPME and Staggered Mesh Ewald Methods.

### 2012-05-02 longRange.hetero/publish/sendfile/main.tex
fix bugs

In this example,  41472 charges are put into a
$14.90\textsf{nm}\times 7.45\textsf{nm}\times 7.45\textsf{nm}$
periodic simulation box. One third of
them are carrying negative charge of $-0.834e$, and the other two thirds
are carrying positive charge of $+0.417e$.
The position of these charges
are randomly generated subjecting to the number density shown in
Fig.~\ref{fig:tmp-rho1}.  The number density of the  positive
charge   is twice as larger as that of the negative charge,
so the
positive and negative charges cancel, and the
system is \emph{locally} neutral. Notice the amount of charges
and the density distributions are intentionally chosen the same as
Example 3~(see section \ref{sec:example3}), 
for an easy comparison.  The only difference is that the positions
of charges are independent  in this example,
while they are correlated in Example 3.
% Both the density distributions are highly
% inhomogeneous, take the positive distribution for example: between 11
% \textsf{nm} and 29 \textsf{nm}, the charge density is
% $1.0\;\textsf{e/nm}^3$, while between 0 \textsf{nm} to 9 \textsf{nm}
% and between 31 \textsf{nm} to 40 \textsf{nm}, the density is
% $0.05\;\textsf{e/nm}^3$.

>>>>

In this example,  41472 charges are put into a
$14.90\textsf{nm}\times 7.45\textsf{nm}\times 7.45\textsf{nm}$
periodic simulation box. One third of
them are carrying negative charge of $-0.834e$, and the other two thirds
are carrying positive charge of $+0.417e$.
The position of these charges
are randomly generated subjecting to the number density shown in
Fig.~\ref{fig:tmp-rho1}.  The number density of the  positive
charge   is twice as large as that of the negative charge,
so the
positive and negative charges cancel, and the
system is \emph{locally} neutral. Notice the amount of charges
and the density distributions are intentionally chosen the same as
Example 3~(see section \ref{sec:example3}), 
for an easy comparison.  The only difference is that the positions
of charges are independent  in this example,
while they are correlated in Example 3.
% Both the density distributions are highly
% inhomogeneous, take the positive distribution for example: between 11
% \textsf{nm} and 29 \textsf{nm}, the charge density is
% $1.0\;\textsf{e/nm}^3$, while between 0 \textsf{nm} to 9 \textsf{nm}
% and between 31 \textsf{nm} to 40 \textsf{nm}, the density is
% $0.05\;\textsf{e/nm}^3$.
